\documentclass[11pt, letterpaper]{article}
\usepackage{resume}  % use my resume style sheet
\usepackage[none]{hyphenat}
\usepackage{microtype}

% \fancyhead[L]{\footnotesize \bfseries Homework 3 \quad \bfseries CS6530 Machine Learning} % set footer
% \fancyfoot[R]{\footnotesize \thepage} % set footer
\fancyfoot[C]{\footnotesize \thepage \; of  \, \pageref{LastPage}}
\geometry{head=1in, bottom=1in, left=1in, right=1in} % set margin
\allowdisplaybreaks  % allow cross-page equations


%--------- document starts here -------------------------
\begin{document}

\begin{tabular}{@{} p{.4\textwidth} p{.6\textwidth} @{}}
   \multirow{4}{*}{{\textbf{\huge XUXIAO LI}}} & 
    LinkedIn: \href{https://www.linkedin.com/in/xuxiaoli1993}{https://www.linkedin.com/in/xuxiaoli1993} \\
     & Personal Website: \href{https://xuxiaoli-1993.github.io}{https://xuxiaoli-1993.github.io} \\
     & xuxiaoli.utah@gmail.com \\
     & 8012096239
\end{tabular}

\vspace{24pt}

% \textbf{Ph.D. with 5 years' experience in physics-based modeling and computation}
% \begin{itemize}[leftmargin=*, labelsep=5mm]
%    \item Expertise in computational fluid dynamics (CFD), heat transfer, and material science.
%    \item Experienced with maintaining, developing, and validating large scientific code.
%    \item Collaborated with physicists and metrologists, coauthored 6 journal articles.
% \end{itemize}

% \vspace{12pt}

\textbf{EDUCATION}

\fullrule

\textbf{University of Utah} \hfill Salt Lake City, Utah

Ph.D., Mechanical Engineering  \hfill May 2021

M.S., Mechanical Engineering  \hfill May 2019

Area of Focus: thermal-fluid and metallurgical modeling for laser-based 3D printing.

Coursework: Computational Fluid Dynamics (CFD), Thermodynamics, Heat Transfer, Numerical Solution of
PDE, Physical Metallurgy, Machine Learning.

\vskip 6pt

\textbf{Tongji University} 
\hfill
Shanghai, China

B.S., Aircraft Manufacturing Engineering \hfill June 2015

Coursework: Solid and Structural Mechanics, Control Theory, Aerodynamics.

\vskip 9pt

\textbf{TECHNICAL SKILLS}

\fullrule

\textit{Programming}: Fortran, C, C++, Python, Matlab, Java.

\textit{High-Performance Computing}: MPI, OpenMP, Linux/Bash, GDB, Valgrind, Intel Profiler.

\textit{Software}: StarCCM+, Abaqus, COMSOL, Tecplot, Paraview, Gmsh. 

% \vskip 3pt

% \begin{tabular}{@{} l l l l l l l @{}}
%    Fortran & Matlab & Linux & MPI & COMSOL & Git & SLURM \\
%    C/C++ & Python & Tecplot & OpenMP & Abaqus & Latex & Gmsh
% \end{tabular}

\vspace{9pt}

\textbf{WORK EXPERIENCE}

\fullrule

\textbf{Global Engineering \& Materials, Inc.} \hfill Princeton, New Jersey

Mechanical Research Engineer \hfill May 2021 -- Present

\begin{itemize}[leftmargin=*, labelsep=5mm]
   \item Developed CFD process models for liquid composite molding and additive friction stir
      deposition with StarCCM+ (porous media, volume-of-fluid, and non-Newtonian flow).
   \item Coordinated meetings with team members to check status, collect data, and assign tasks.
      Assisted proposal writing for government-funded programs.
\end{itemize}

\vspace{3pt}

\textbf{Ph.D. RESEARCH EXPERIENCE}

\fullrule

\textbf{CFD Software Development} \hfill Nov. 2016 -- May 2021
\begin{itemize}[leftmargin=*, labelsep=5mm]
   \item Maintained an in-house CFD code, GEMS (in Fortran, over 25000 lines), for both compressible
      and incompressible flows, featuring the finite volume method, unstructured mesh, and MPI.
   \item Developed 5 new modules (level-set and finite-difference method, over 15000 lines) to grow
      capabilities for multiphase flow, free-surface tracking, and fluid-structure interaction.
   \item Identified and solved numerical issues such as boundary condition definition,
      discretization accuracy, and parallel communication bottlenecks.
   \item Conducted benchmarking ($>$ 15 test problems), wrote documentation, and provided training.
\end{itemize}

\vspace{3pt}

\textbf{Transient Dynamics in Laser Welding} \hfill Nov. 2018 -- Oct. 2020
\begin{itemize}[leftmargin=*, labelsep=5mm]
   \item Developed a multiphysics model (based on GEMS) that simulates the laser-metal interaction,
      melting and evaporation, molten pool flow, and gas dynamics in laser welding.
   \item Coordinated with experimentalists to compare the simulation with
      X-ray imaging data.
   \item Quantified the thermal field and fluid dynamics to understand the pore (defect) formation.
      Provided design guidance (e.g., optimizing process parameters) to mitigate defects.
\end{itemize}

\vspace{3pt}
\textbf{Powder-gas Interaction in Laser Powder Bed Fusion} \hfill Sep. 2019 -- Dec. 2020
\begin{itemize}[leftmargin=*, labelsep=5mm]
   \item Integrated a discrete element method module into the welding model to simulate the
      interaction between micron-size powders and high-speed gas flow in metal 3D printing.
   \item Developed scripts to automate over 150 simulations. Verified the model with lift
      coefficients and Strouhal number. Validated the model with X-ray imaging data.
   \item Post-process large data ($>$ 5 TB). Characterized the modes of powder-gas interaction to
      improve the understanding of powder spattering (defects).
   \item Numerically investigated the applicability of a novel process design, i.e., changing the
      ambient pressure in the build chamber. Predicted the design's effects on powder-gas behaviors.
\end{itemize}

\vspace{3pt}

%\textbf{Finite Element Analysis for Laser Bending} \hfill Sep. 2019 -- Dec. 2019
%\begin{itemize}[leftmargin=*, labelsep=5mm]
%   \item Developed a thermo-mechanical model using Abaqus to simulate the thermal stress and strain
%      evolution in the laser bending of aluminum plates.
%   \item Conducted parametric studies for process design to achieve maximum bending angle with
%      minimum power input.
%\end{itemize}

\textbf{Deep Learning for Laser Absorption by Metal Surface} \hfill Jan. 2020 -- April 2020
\begin{itemize}[leftmargin=*, labelsep=5mm]
   \item Extracted laser absorption distribution on the surface of molten metal from the laser
      welding model, as the training and validation data sets.
   \item Applied convolutional neural network algorithms using Tensorflow to predict the laser
      absorption distribution for random molten metal surfaces in laser welding.
\end{itemize}

\vspace{3pt}

\textbf{Metallurgical Modeling for Direct Energy Deposition} \hfill Nov. 2016 -- May 2018
\begin{itemize}[leftmargin=*, labelsep=5mm]
   \item Developed a process model that simulates the thermal history and surface evolution in
      direct energy deposition processes.
   \item Implemented a cellular automata algorithm with a hybrid MPI-OpenMP parallelization (in
      C/C++) to simulate the grain melting, nucleation, and growth. 
   \item Conducted simulations to identify nucleation conditions to tailor distinct grain
      morphology, e.g., small equiaxed grains and large columnar grains.
\end{itemize}

\vspace{3pt}

\textbf{Laser Absorption by Powder Bed} \hfill Sep. 2015 -- Aug. 2016
\begin{itemize}[leftmargin=*, labelsep=5mm]
   \item Implemented a rain-dropping algorithm to generate randomly packed beds of powders as in
      typical metal 3D printing processes.
   \item Implemented the ray-tracing algorithm to simulate the multiple reflections of a laser beam
      on the surfaces of powders.
   %\item Conducted parametric studies on the effects of powder size, powder bed thickness, and powder
   %   material on the laser absorption distribution within the powder bed.
\end{itemize}

\vspace{9pt}

\textbf{SELECTED PUBLICATIONS} \hfill (full list:  
\href{https://xuxiaoli-1993.github.io/publications.html}
{https://xuxiaoli-1993.github.io/publications.html})

\fullrule

\begin{enumerate}[leftmargin=*, labelsep=4mm]
   \item \textbf{Li, X.}, Guo, Q., Chen L., Tan, W., 2021. Quantitative investigation of gas flow,
      powder-gas interaction, and powder behavior under different ambient pressure levels in laser
      powder bed fusion.  International Journal of Machine Tools and Manufacture, 170, 103797.

   \item \textbf{Li, X.}, Zhao, C., Sun, T., Tan, W., 2020. Revealing transient powder-gas
      interaction in laser powder bed fusion process through multi-physics modeling and high-speed
      synchrotron x-ray imaging. Additive Manufacturing, 35, p.101362. 

   \item Zhao C., Parab, N.D., \textbf{Li, X.}, Fezzaa, K., Tan, W., Rollett, A.D., Sun. T., 2020.
      Critical instability at moving keyhole tip generates porosity in laser melting. Science,
      370(6520), pp.1080-1086.

   % \item \textbf{Li, X.}, Tan, W., 2020. Numerical modeling of powder-gas interaction relative to
   %    laser powder bed fusion process. Journal of Manufacturing Science and Engineering, 143(5), pp.
   %    054502.

   \item Kouraytem, N., \textbf{Li, X.}, Cunningham, R., Zhao, C., Parab, N., Sun, T., Rollett,
      A.D., Spear, A.D., Tan, W., 2019. Effect of laser-matter interaction on molten pool flow and
      keyhole dynamics. Physical Review Applied, 11(6), p.064054.

   % \item Zhao, C., Guo, Q., \textbf{Li, X.}, Parab, N., Fezzaa, K., Tan, W., Chen, L., Sun, T.,
   %    2019. Bulk-explosion-induced metal spattering during laser processing. Physical Review X,
   %    9(2), p.021052.

   \item \textbf{Li, X.}, Tan, W., 2018. Numerical investigation of effects of nucleation mechanisms
      on grain structure in metal additive manufacturing. Computational Material Science, 153,
      pp.159-169.

   %\item Herriott, C.F., \textbf{Li, X.}, Kouraytem, N., Tari, V., Tan, W., Anglin, B.S., Rollett, A.D.,
   %   Spear, A.D., 2018. A multi-scale, multi-physics modeling framework to predict spatial
   %   variation of properties in additive-manufactured metals. Modelling and Simulation in
   %   Materials Science and Engineering, 27, p. 025009.
\end{enumerate}


\end{document}






